---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# JGNsc

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/biodatascience/homework-meichendong.svg?branch=master)](https://travis-ci.com/biodatascience/homework-meichendong)
[![CRAN status](https://www.r-pkg.org/badges/version/JGNsc)](https://CRAN.R-project.org/package=JGNsc)
<!-- badges: end -->

Joint Gene Network Construction by Single Cell RNA Sequencing Data under Multiple Conditions

## Citation

## Installation
The development version from [GitHub](https://github.com/):
```{r}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("meichendong/JGNsc")
```

The manuscript is in preparation.


## Example

```{r example}
library(JGNsc)
## basic example code
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

## FAQs / Notes
......
